### 2020-08-03 thesis/chap_1.tex
udpates disc 1

For instance, by looking at a simple metric (mean flow), we have shown that some species will react more simply and linearly than others. We saw a simple and linear response to change for species which, in our model, had dependency on forest types that were expected to be impacted only by land use change, such as the redbacked salamander and the wood frog. This was not the case for species which are dependent on coniferous forests or mixed type forests, more at risk from climate change, and therefore more likely to suffer from the interaction of the two drivers. The results of our simple reforestation scenario highlights that it might be hard to plan for species with different needs. Restoration actions remain very uncertain: the impact of reforesting will depend on what is replanted and where it is replanted. Forest management could turn out to be critical for species dependent on forest types more vulnerable to a changing climate. A final insight is given by the width of difference between the outcome of the two scenarios for each of the species. The fact that this difference is larger for some species  than for others possibly indicates more uncertainty with regards to the real future trajectory of those species at the 2100 horizon.

@@

% Limitations
This work constitutes progress over past projects on which this work is built. We covered a larger extent, improved on the land use change model from \cite{albert_applying_2017}, and demonstrated the flexibility of our framework for supporting alternative scenarios. But besides the important methodological contribution of this chapter, it is not without limitations. We see four main axes along with this work is limited and could be improved. To begin, different steps of the modelling process were limited computationally by time and computing resources, which led us to having to aggregate the raw data from a 30 meter resolution to a 90 meter resolution, leading to a loss of data and a loss in the quality of the data. A major consequence of this aggregation is that roads, which constitute an import barrier to connectivity, were not properly aggregated causing multiple arbitrary holes in the road network, severely limiting the ecological realism of the results presented in this thesis, and compromising the reliability of the flow surfaces obtained through Circuitscape. In future iteration of this work, a proper road network will need to be rasterized and added onto our resistance surfaces.

@@

A third limitation is found in the habitat suitability analysis. The steps and parameters of the analysis were modified from \cite{rayfield_priorisation_2018} to fit our dataset and those modifications prevent us from comparing our results to their results. The analysis is also limited in the sense that multiple factors that were originally included in Rayfield's original analysis are not taken into account. For instance, the fact that black bear habitat would receive a negative multiplier if it is close to urban land is not included in our analysis (whereas it was included in Rayfield's), and should indicate that the results observed for the bear might be overestimated. Similarly, in Rayfield's analysis, the wood frog is dependent on wetlands and habitat receives a negative multiplier if it is far from wetland. Including this might change the response of this species.

@@

We successfully integrated a potential functional connectivity model for 5 umbrella species with a land use and climate change model, using circuit theory as our main method of analysis. We analyzed simple properties of the resulting flow surfaces and looked at the differences in the species response. Species who depend on forest types that are both vulnerable to land use and climate change responded in more complex, less linear, and less consistent ways than species who only depend on forest types that are mostly threatened by land use changes. While improving on related past work in the region, we open the door for other methods of flow analysis and for a more rigorous implementation of the modelling process. We hope this work can serve as a reminder that connectivity conservation planning needs to better take into account the joint effects of interacting drivers such as land use and climate change.

>>>>

For instance, by looking at a simple metric (mean flow), we have shown that some species will react more simply and linearly than others. We saw a simple and linear response to change for species which, in our model, had dependency on forest types that were expected to be impacted only by land use change, such as the Redbacked salamander and the Wood frog. This was not the case for species which are dependent on coniferous forests or mixed type forests, more at risk from climate change, and therefore more likely to suffer from the interaction of the two drivers. The results of our simple reforestation scenario highlights that it might be hard to plan for species with different needs. Restoration actions remain very uncertain: the impact of reforesting will depend on what is replanted and where it is replanted. Forest management could turn out to be critical for species dependent on forest types more vulnerable to a changing climate. A final insight is given by the width of difference between the outcome of the two scenarios for each of the species. The fact that this difference is larger for some species  than for others possibly indicates more uncertainty with regards to the real future trajectory of those species at the 2100 horizon.

@@

% Limitations
This work constitutes progress over past projects on which this work is built. We covered a larger extent, improved on the land use change model from \cite{albert_applying_2017}, and demonstrated the flexibility of our framework for supporting alternative scenarios. But besides the important methodological contribution of this chapter, it is not without limitations. We see four main axes along with this work is limited and could be improved. To begin, different steps of the modelling process were limited computationally by time and computing resources, which led us to having to aggregate the raw data from a 30 meter resolution to a 90 meter resolution, leading to a loss of data and a loss in the quality of the data. A major consequence of this aggregation is that roads, which constitute an important barrier to connectivity, would have been broken up by the aggregation process. Instead, they had to be aggregated out of the raster surface and a road network was rasterized and overimposed  onto the newly aggregated raster. They led us on only to keep major roads, which is still a limitation given the assumption that roads 90m wide represent accurately the extent to which they represent a barrier to connectivity. One possible improvement in that method would be to aggregate all roads but to weight the resistance differently based on the type.

@@

A third limitation is found in the habitat suitability analysis. The steps and parameters of the analysis were modified from \cite{rayfield_priorisation_2018} to fit our dataset and those modifications prevent us from comparing our results to their results. The analysis is also limited in the sense that multiple factors that were originally included in Rayfield's original analysis are not taken into account. For instance, the fact that Black bear habitat would receive a negative multiplier if it is close to urban land is not included in our analysis (whereas it was included in Rayfield's), and should indicate that the results observed for the bear might be overestimated. Similarly, in Rayfield's analysis, the Wood frog is dependent on wetlands and habitat receives a negative multiplier if it is far from wetland. Including this might change the response of this species.

@@

We successfully integrated a potential functional connectivity model for 5 umbrella species with a land use and climate change model, using circuit theory as our main method of analysis. We analyzed simple properties of the resulting flow surfaces and looked at the differences in the species response. Species who depend on forest types that are both vulnerable to land use and climate change responded in more complex, less linear, and less consistent ways than species who only depend on forest types that are mostly threatened by land use changes. While improving on related past work in the region, we open the door for other methods of flow analysis and for a more rigorous implementation of the modelling process. We hope this work can serve as a reminder that connectivity conservation planning needs to better take into account the joint effects of interacting drivers such as land use and climate change.\\
